Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-01-03 Manuscript Analyses/manuscript_analysis.Rmd
Initial Intelligibility Models

## Function for model training
training <- function(data, method, int) {
  form = if (isTRUE(int)) {
    d2 = model.matrix(pwc ~ . * ., data = data)[, -1] %>%
      as_tibble() %>%
      janitor::clean_names()
    d2$pwc = data$pwc
  } else {
    d2 = data
    train(
      pwc ~ ., 
      data = d2, 
      preProcess = c("center", "scale"),
      method = method, 
      trControl = caret::trainControl(
        method = "repeatedcv",
        number = 5,
        repeats = 10
    ))
  }
}

@@

>>>>

## Function for model training
training <- function(data, method, int) {
  form = if (isTRUE(int)) {
    d2 = model.matrix(pwc ~ . * ., data = data)[, -1] %>%
      as_tibble() %>%
      janitor::clean_names()
    d2$pwc = data$pwc
  } else {
    d2 = data
  }
    train(
      pwc ~ ., 
      data = d2, 
      preProcess = c("center", "scale"),
      method = method, 
      trControl = caret::trainControl(
        method = "repeatedcv",
        number = 5,
        repeats = 10
    )
  )
}

@@

p2

in_and_out <- function(mods, speaker) {
  out_sample_r2 = map_dbl(mods, ~max(.x$results$Rsquared))
  out_sample_rmse = map_dbl(mods, ~min(.x$results$RMSE)) 
  tibble(
    speaker = speaker,
    mods = c("Main Effects", "Interactions"),
    out_sample_r2,
    out_sample_rmse
  )
}

AM1_initial_mod <- in_and_out(mods1, "Ataxic")

PDM10_initial_mod <- in_and_out(mods2, "PD")

initial_mods <- rbind(AM1_initial_mod, PDM10_initial_mod)

initial_mods %>%
  gt::gt() %>%
  cols_label(speaker = "Speaker",
             mods = "Model Specification",
             out_sample_r2 = "R\U00B2",
             out_sample_rmse = "RMSE")

t_for_diff <- function(mods){
  samps = resamples(list(
    main = mods[[1]],
    int = mods[[2]]
  ))
  summary(samps)
  diff(samps) %>%
    summary()
}

t_for_diff(mods1)
t_for_diff(mods2)

effect_data <- function(mod){
  mod[[2]]$trainingData %>%
    mutate(preds = predict(mod[[2]]))
}

effect_plot <- function(mod, var, var2 = NULL, int = TRUE, num = 5) {
  dat = effect_data(mod)

  if (isFALSE(int)){
    dat %>%
      ggplot() +
      aes(x={{var}}, 
          y = .outcome) +
      geom_point() +
      geom_smooth(method = "lm")
  } else {
    dat %>%
      ggplot() +
      aes(x = {{var}},
          y= .outcome,
          group = cut_interval({{var2}}, num),
          color = cut_interval({{var2}}, num)) +
      geom_point() +
      geom_smooth(method = "lm") +
      theme(legend.position = "bottom")
  }
}

# AM1 Effect Plots

effect_plot(mods1, pic_seq_c, best_win)
effect_plot(mods1, best_win, pic_seq_c)
effect_plot(mods1, best_win, int = F)
effect_plot(mods1, list_sort_c, vocab_c)
effect_plot(mods1, vocab_c, list_sort_c)
effect_plot(mods1, list_sort_c, pattern_c)
effect_plot(mods1, pattern_c, list_sort_c)

# PDM10 Effect Plots

effect_plot(mods2, vocab_c, pattern_c)
effect_plot(mods2, pattern_c, vocab_c)
effect_plot(mods2, best_win, int = F)
effect_plot(mods2, flanker_c, best_win)
effect_plot(mods2, best_win, flanker_c)
effect_plot(mods2, list_sort_c, pattern_c)
effect_plot(mods2, pattern_c, list_sort_c)
effect_plot(mods2, vocab_c, pic_seq_c)
effect_plot(mods2, pic_seq_c, vocab_c)
effect_plot(mods2, card_sort_c, vocab_c)
effect_plot(mods2, vocab_c, card_sort_c)
